\vfill
\pagebreak


%  Label worksheets by \thechapter.W
\renewcommand{\thesection}{\thechapter.W}


\section{Polarization of Light Worksheet}
\subsection{Data \& Calculations}

\subsubsection{Preliminaries}

(Follow procedure in Section 8.4.1 of Lab Manual (p 148))
\vspace*{.5cm}

\noindent
Measure the voltage of the photodiode $V$ for {\it five} well-separated polarizer
angles $\theta$
{\bf between $0^{\circ}$ and $90^{\circ}.$} Enter these with uncertainties in the table
below.

\begin{table}[htb]
\begin{center}
\begin{tabular}{|c|c|}
\hline
\multicolumn{2}{|c|}{Measurements of $V$ vs. $\theta$} \\
\hline
Voltage ($V$) & Angle ($\theta$)  \\
\hline
\hspace*{3cm} & \hspace*{3cm}  \\
&   \\
\hline
&   \\
&  \\
\hline
& \\
& \\
\hline
&  \\
&  \\
\hline
&  \\
&  \\
\hline
\end{tabular}
\end{center}
\caption{$V$ vs. $\theta$ measurements for single polarizer}
\label {tab:PO:1lens}
\end{table}

\noindent
Plot $V$ vs. $\theta$ with errorbars.

\subsubsection{Polarized Light and a Polarizer}

(Follow procedure in Section 8.4.2 of Lab Manual (pp 148-9))
\vspace*{.5cm}

\noindent
{\bf Note:}
In this section you should set the first polarizer to $0^{\circ}$ and leave it there.
\vspace*{.5cm}
\noindent 
Now measure the voltages $V$ of the photodiode for each of the angles of the second 
polarizer $\theta _{12}$ set at $10^{\circ}$ increments 
{\bf between $0^{\circ}$ and $90^{\circ}.$} Enter these values with uncertainties in
the table below. 

\begin{table}[htb]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{Measurements of $V$ vs. $\theta _{12}$ for
 Two Polarizers.} \\
\hline
Voltage ($V$) & Angle ($\theta _{12}$) & & Voltage ($V$) & Angle ($\theta _{12}$) \\
\hline
\hspace*{3cm} & \hspace*{3cm} & \hspace*{.3cm} & \hspace*{3cm} & \hspace*{3cm} \\
& & & & \\
\hline
& & & & \\
& & & & \\
\hline
& & & & \\
& & & & \\
\hline
& & & & \\
& & & & \\
\hline
& & & & \\
& & & & \\
\hline
\end{tabular}
\end{center}
\caption{$V$ vs. $\theta _{12}$ measurements for two polarizers.}
\label {tab:PO:2lens}
\end{table}

\noindent
Plot $V$ vs. cos$^2 \theta _{12}$ with errorbars. Show your calculation for the
uncertainty in cos$^2 \theta _{12}$ in the space below.

\noindent
{\it Sample Calculations:}

\newpage

\subsubsection{Crossed Polarizers}

(Follow procedure in Section 8.4.3 of Lab Manual (p 149))
\vspace*{.5cm}

\noindent
In this section, you should set the first polarizer to $0^{\circ}$ and the third
polarizer to $90^{\circ},$ and leave them there.
\vspace*{.5cm}

\noindent 
Now measure the voltages $V$ of the photodiode for each of the angles of the second 
polarizer $\theta _{12}$ set at $10^{\circ}$ increments 
{\bf between $0^{\circ}$ and $90^{\circ}.$} Enter these values with uncertainties in
the table below.
 
\begin{table}[htb]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{Measurements of $V$ vs. $\theta _{12}$ for
 Three Polarizers.} \\
\hline
Voltage ($V$) & Angle ($\theta _{12}$) & & Voltage ($V$) & Angle ($\theta _{12}$) \\
\hline
\hspace*{3cm} & \hspace*{3cm} & \hspace*{.3cm} & \hspace*{3cm} & \hspace*{3cm} \\
& & & & \\
\hline
& & & & \\
& & & & \\
\hline
& & & & \\
& & & & \\
\hline
& & & & \\
& & & & \\
\hline
& & & & \\
& & & & \\
\hline
\end{tabular}
\end{center}
\caption{$V$ vs. $\theta _{12}$ measurements for three polarizers.}
\label {tab:PO:3lens}
\end{table}

Plot $V$ vs. $\theta _{12}$ with errorbars.

\newpage

\subsection{Discussion}

Is the light from the desk lamp polarized before it encounters a polarizer? Discuss
how you can determine this from the plot you made from the data you took in the first
part of the procedure.
\vspace*{2cm}

\noindent
Is the data you took in the second part of the procedure consistent with Malus' Law the theoretical relationship between 
the transmitted intensity and the initial intensity for polarized light passing
through a polarizer at some relative angle)?
Explain.
\vspace*{2cm}

\noindent
How can the intensity of the light passing through three polarizers be non-zero when
the first and third polarizers are perpendicular? Assume ideal experimental conditions.
\vspace*{2cm}

\noindent
On pp 149-50 of the Lab Manual, there is an additional question. Answer this in the
space below.



% Go back to ordinary section numbering
\renewcommand{\thesection}{\thechapter.\arabic{section}}



